---
title: 'Data 607: Week 3 Assignment'
subtitle: 'R Character Manipulation and Date Processing'
author: "Mustafa Telab"
date: "9/9/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r, results='hide', message=FALSE}
library(RCurl)
library(stringr)
library(tidyverse)
```

# #1. 
Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"


```{r}

getfile <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv") 
majors <- read.csv(text = getfile)
data_or_stat <- majors %>%
  filter(str_detect(Major, "DATA|STATISTICS"))
print(data_or_stat)
```
# #2 
Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
needtoclean <-' "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry" '

cleaned <- needtoclean %>%
  str_split(boundary("word"))%>%
  .[[1]]%>%
  str_subset("[^\\d]")

print(cleaned)
```
The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

# #3 
Describe, in words, what these expressions will match:

(.)\1\1: The character that directly preceeds \1\1.

"(.)(.)\\2\\1": First character followed by two of the second, followed by the first; all within double quotation ex. "xyyx"

(..)\1: The two characters that directly proceed \1.

"(.).\\1.\\1": First character, followed by any character, then first character, then any character, the first character; all within double quotation.  ex "xyxyx"

"(.)(.)(.).*\\3\\2\\1": First three characters, then anything, ending with the first three characters in reverse order; all within double quotation. ex."xyzaddazyx"

```{r}

```
# #4 
Construct regular expressions to match words that:

Start and end with the same character.
```{r}
str_view(fruit, "^(.).*\\1$", match = TRUE)

```

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r, message=FALSE, warning=FALSE}
str_view(fruit, "(.)(.).*\\1\\2", match = TRUE)
```

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r , message=FALSE}
str_view(fruit, "(.).*\\1.*\\1", match = TRUE)
```

